Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-02 WRITEUP/ms.tex

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ ---accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$.  \MM{Give the color coding somewhere.} 
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).   \MM{For consistency with
  Figure 1, label as ``Accreting'' rather than ``Accretion'' phase. I
  am inclined to leave the pressure confinement curves off of the
  final plot.}
\label{fig:larsons_single}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs identified in the accreting phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF
reported by \citet{Kauffmann10b}. Star symbols are color-coded by
increasing $n_{\rm cut}$. \MM{which direction? White high or blue
  high?} Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
%same as \Fig{larsons_single}.  
Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
\label{fig:MR}}
%mm}
\end{figure*}

@@

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
thickness of its disk (via $\sigma_z$), some of these MCCs are
consistent with  $Q_{\rm eff} > 1$. 
\MM{Is your $Q_{\rm eff}$ based on your equation 11?  If not, you
  should probably show it's value explicitly, or else remove that
  section of the explanation [you don't want to leave the ``rifle on
  the wall''.]}.
This demonstrates the importance of accounting for stellar contribution and disk thickness 
when examining the stability of molecular gas structures.
This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
that are preferentially being imaged at high resolution with ALMA.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).

>>>>

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
MCCs (star symbols) identified in the two most extreme evolutionary
stages of \flower\ ---accreting phase (left) and starburst phase
(right). Star symbols are color-coded by the density thresholds
$n_{\rm cut}$, as illustrated by the colorbar.
Data points in the $\alpha_{\rm vir}$-mass figure are taken from
\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
(see Fig 4 of \citealt{Kauffmann17b}).   \MM{For consistency with
  Figure 1, label as ``Accreting'' rather than ``Accretion'' phase. I
  am inclined to leave the pressure confinement curves off of the
  final plot.}
\label{fig:larsons_single}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs identified in the accreting phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF
reported by \citet{Kauffmann10b}. Star symbols are color-coded by
increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
%same as \Fig{larsons_single}.  
Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
\label{fig:MR}}
%mm}
\end{figure*}

@@

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
thickness of its disk (via $\sigma_z$), some of these MCCs are
consistent with  $Q_{\rm eff} > 1$. 
\MM{Is your $Q_{\rm eff}$ based on your equation 11?  If not, you
  should probably show it's value explicitly, or else remove that
  section of the explanation [you don't want to leave the ``rifle on
  the wall''.]}. \DL{ this is based on Eqn 12.}
This demonstrates the importance of accounting for stellar contribution and disk thickness 
when examining the stability of molecular gas structures.
This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
that are preferentially being imaged at high resolution with ALMA.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).
